Water Management

### 2020-02-22 Paper/paper.tex
resolve TODOs
proper formatting for new sections

% TODO do we need a abstract?
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

@@

which equals to finding the column $aux$ that maximizes the expected value over all states (TODO: kann man das so sagen?).
We repeat this step over and over again until the our value function $V$ converges.
In our case the function converges, if the norm of the difference between $V'$ and $V$ falls below a certain tolerance value) \\

@@

Due to the fact, that our water level highly depends on the randomly distributed rainfalls that fill the reservoir at end of each period, it is not possible to find a steady state in which the water level does not change at all. % TODO: auch noch evaporation nennen?

@@

% TODO changed irrigation policy?

@@

%TODO update figures

@@

\section{Conclusion}
%TODO content
\printbibliography

>>>>

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles
\newcommand{\sectionbreak}{\clearpage}

@@

which equals to finding the column $aux$ that maximizes the expected value over all states.
We repeat this step over and over again until the our value function $V$ converges.
In our case the function converges, if the norm of the difference between $V'$ and $V$ falls below a certain tolerance value) \\

@@

Due to the fact, that our water level highly depends on the randomly distributed rainfalls that fill the reservoir at end of each period, it is not possible to find a steady state in which the water level does not change at all. 

@@

Since the mean stays constant within the analyzed comparison, the value function does not change.

@@

@@

\section{Conclusion}
%TODO content
\clearpage
\printbibliography
